\texttt{SuperScreen}: An open-source package for simulating the magnetic response of 2D superconductors

### 2021-08-02 main_cpc.tex
Updates from Overleaf

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
  \caption{A subfigure}
  \label{fig:circular_ring_mesh}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
  \caption{A subfigure}
  \label{fig:square_ring_mesh}
\end{subfigure}
\caption{A figure with two subfigures}
\label{fig:ring_mesh}
\end{figure}

After the mesh is generated, the matrices and vectors described in Section~\ref{section:implementation} can be computed and one can begin solving models.

>>>>

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
%   \caption{A subfigure}
  \label{fig:circular_ring_mesh}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
%   \caption{A subfigure}
  \label{fig:square_ring_mesh}
\end{subfigure}
\caption{Device geometry and mesh for a circular and square ring generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}.}
\label{fig:ring_mesh}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
%   \caption{A subfigure}
  \label{fig:circular_ring_mesh}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
%   \caption{A subfigure}
  \label{fig:square_ring_mesh}
\end{subfigure}
\caption{Device geometry and mesh for a circular and square ring generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}.}
\label{fig:ring_mesh}
\end{figure}
After the mesh is generated, the matrices and vectors described in Section~\ref{section:implementation} can be computed and one can begin solving models.
